---
title: "How to customize shiny apps"
author: "Lena Hubig"
date: "29 8 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## User Interface HTML

* Call R functions to assemble HTML
* The HTML that builds the user interface in your app: `fluidPage` 
* Use `input*()`and `output*()` functions to add reactive content
* save the ouput to `ui`

## Static Content

HTML tags are stored in list of functions `tags$h1()`, `tags$a()`

* named arguments appear as tag attributes
* unnamed arguments appear inside the tags

can also pass raw HTML with HTML("")

## Create a layout

fluidRow()
* adds row to the grid. Each new row goes below the previous one

column()
* adds columns within a row. Each new columns goes to the left of the previous column
* specify the width and offset of each column out of 12

```{r}
ui <- fluidPage(
  fluidRow(
    column(3),
    column(5,
           sliderIput(...))
  ),
  fluidRow(
    column(4, offset = 8,
           plotOutput("hist"))
  )
)
```

## Layers of panels

Panels to group multiple elements into a single unit with its own properties

`wellPanel()`
groups elements into a grey "well"

* absolutePanel: Panel position set rigidly (absolutely), not fluidly
* conditionalPanel: A JavaSript expression determines whether panel is visible or not
* fixedPanel: Panel is fixed to browser window and does not scroll with the page
* headerPanel: Panel for the apps title, used with pageWithSidebar()
* inputPanel(Panel with grey background, uistable for grouping inputs)
* mainPanel: Panel for displaying output, usew with pageWithSidebar()
* navlistPanel(): Panel for displaying multiple stacked tabPanels(). Uses sidebar navigation
* sidebarPanel: Panel for displaying a sidebar of inputs, used with pageWithSidebar()
* tabPanel: Stackable panel. Used with navlistPanel() and tabsetPanel()
* tabsetPanel: Panel for displaying multiple stacked tabPanels(). Uses tap navigation
* titlePanel(): Panel for apps title, used with pageWithSidebar()
* wellPanel: Panel with grey background

* Panels group elements into a single unit for aesthetic or functional reasons
* Use tabPanel() to create a stackable panel
* Use tabseltPanel() to arrange tab panels into a stack with tab navigation

## Prepackaged layout

sidebarLayout() 
* used with sidebarPanel() and mainPanel() to divide app into two sections

navbarPage()
combines tabs into a single page
navbarPage() replaces fluidPage(), requires title

navbarMenu()
combbines tab links into a dropdown menu for navbarPage()

```{r}
navbarPage(title = "Title",
           tabPanel("tab1", "contents"),
           navbarMenu(title = "More",
                      tabPanel("tab2", "content"),
                      tabPanel("tab3", "content")))
```

## CSS


